---
title: "Discussion Board Week # 12"
author: "Al Haque"
date: '2022-11-09'
output: html_document
---

### Info:
This dataset contains a hourly/daily summary for Szeged, Hungary area, between 2006 and 2016. With columns that include,
time,summary,precipType,temperature,apparentTemperature,humidity,windSpeed,windBearing,visibility,loudCover,pressure.
Link to Dataset: <https://www.kaggle.com/datasets/budincsevity/szeged-weather> 


```{r}
library(tidyverse)
Data <- read.csv("https://raw.githubusercontent.com/AldataSci/Multiple-Linear-Regression-attempt/main/weatherHistory.csv",header=TRUE)
head(Data)
```

```{r}
## Clean out the null data types: 
NewD <-Data %>%
  select(-Daily.Summary,-Loud.Cover) %>%
  filter(Precip.Type != "null")

```

```{r}
## Convert precip.type into numerical representations:
NewD$Precip.Type <- as.character(NewD$Precip.Type)
NewD$Precip.Type[NewD$Precip.Type == "rain"] <- 0
NewD$Precip.Type[NewD$Precip.Type == "snow"] <- 1
NewD$Precip.Type <- as.integer(NewD$Precip.Type)

```

```{r}
## wanted to change the weather summary into numerical representation as well but its too many entries to change.. 
unique(NewD$Summary)
```
```{r}
## Quadratic Variable (Double the WindSpeed)
Wind_spd <- NewD$Wind.Speed..km.h.^2

## Dichomtus vs QUantiative Interaction:
Precip_Wind <- Wind_spd * NewD$Precip.Type
```

```{r}
## Making a model: 
## Predict the temperature with humidity,wind_sped,Precip.wind
weather.lm <- lm(Temperature..C.~Wind_spd + Precip_Wind + Humidity,data=NewD)
summary(weather.lm)
```

```{r}
## Residual analysis This doesn't look good 
plot(weather.lm$fitted.values, weather.lm$residuals, xlab="Fitted Values", ylab="Residuals", main="Residuals vs. Fitted", col = "red")
abline(h=0)
```
```{r}
qqnorm(weather.lm$residuals, col = "blue")
qqline(weather.lm$residuals, col = "darkblue")
```

### Conclusion: 
The model doesn't look that good according to the residual analysis, we can see that the variability in the fitted residuals are all around the same values which is a sign that it is not a good model, in the qq plot we can see both tails skewing especially the left tail not being normally distributed.. The adjusted R2 explains 46% of the variability in temperature. We also see a very small F stat and all the predictors are significant. The equation according to the model is: 

$$
Temperature = 35.54 -0.00357 * wind_spd -0.02913 * Precip_wind - 30.73 * Humidity 
$$